Put Title here

### 2018-06-27 General WLD combinatorics.tex
some pictures added and material involving protecting sets fixed

\pgfmathsetmacro{\n}{#1}
\pgfmathsetmacro{\radius}{#2}
\pgfmathsetmacro{\angle}{360/\n}
    \foreach \i in {1,2,...,\n} {
      \pgfmathsetmacro{\x}{\angle*\i}
        \draw[-,shorten >=-\radius*0.1 cm,shorten <=-\radius*0.1 cm]  (\x:\radius cm)-- (\x + \angle: \radius cm);
    }

\draw (\angle:\radius) node {$\bullet$};
}

@@

\begin{scope}
\clip (\angle*\r:\radius) -- (\angle + \angle*\r:\radius) -- (\angle*\s:\radius) -- (\angle + \angle*\s:\radius) -- (\angle*\r:\radius);
\draw[propagator] (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius) -- (\angle*\s + \angle/2 + \bumps*\perturbe:\radius);
\end{scope}
}

@@

@@

\begin{eg}
Note that since this is an equivalence relation, we may find that two Wilson loop diagrams are equivalent, even if they do not have complements of (non-trivial) exact subdiagrams in common. Consider the following three Wilson loop diagrams,
\bas
W_1 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{8}{1.5}
	\drawnumbers
	\drawprop{1}{0}{4}{0}
	\drawprop{2}{0}{4}{-1}
    \drawprop{5}{0}{8}{0}
    \drawprop{5}{1}{7}{0}
		\end{scope}
	\end{tikzpicture} \quad
W_2 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{8}{1.5}
	\drawnumbers
	\drawprop{1}{0}{4}{0}
	\drawprop{2}{0}{4}{-1}
    \drawprop{5}{0}{8}{0}
    \drawprop{6}{0}{8}{-1}
		\end{scope}
	\end{tikzpicture} \quad
W_3 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{8}{1.5}
	\drawnumbers
	\drawprop{1}{0}{4}{0}
	\drawprop{1}{1}{3}{0}
    \drawprop{5}{0}{8}{0}
    \drawprop{6}{0}{8}{-1}
		\end{scope}
	\end{tikzpicture} .
\eas

@@

\begin{eg}
For example, ordering the propagators of $W_1$ above as follows: \bas (1,4), \, (2,4), \, (5,7), \, (5,8) \eas we may write
\bas C(W_1) = \left(
\begin{array}{cccccccc}
c_{1,1} & c_{1,2} & 0 & c_{1,4} & c_{1,5} & 0 & 0 & 0 \\
0 & c_{2,2} & c_{2,3} & c_{2,4} & c_{2,5} & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & c_{3,5} & c_{3,6} & c_{3,7} & c_{3,8} \\
c_{4,1} & 0 & 0 & 0 & c_{4,5} & c_{4,6} & 0 & c_{4,8}  \\
\end{array}
\right) \;.\eas

@@

***draw some examples***

@@

@@

If $n=2$, then $t$ has two connected componenents. Therefore, $t$ corresponds to a propagator that connects two non-adjacent edges. Therefore, the trivial triangulation is a trivial exact subdiagram.

@@

\begin{enumerate}
\item Fix a vertex $a \in [n]$. Set $i:=a$ and $I_a = \emptyset$.
\item While $\cP \neq \emptyset$, perform the following steps.
\begin{enumerate}
\item \textbf{Step $i$ for vertex $a$}: If $\Prop(i) \neq \emptyset$ in $W$, write $I_a = I_a \cup i$. Let $p \in \Prop(p)$ be the clockwise most propagator supported on $i$. Write $W = (\cP \setminus p, n)$.
\item If $Prop(i) = \emptyset$ do nothing.
\item Increment $i$ by 1 and repeat from (a).
\end{enumerate}
\end{enumerate}
\end{algorithm} \note{I don't like how this is written. Any ideas?}

@@

\begin{dfn}\label{protect dfn}
Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex. For $p= (i,j) \in \cP$ an a propagator of $W$  and $v \in \{i, j\}$ (or $w \in \{i+1, j+1\}$)a vertex of $W$, let $P_{v}$ (or $P_w$) to be a \emph{protecting set of $p$ at $v$ (or $w$) at $a$} be a set of up to $3$ propagators defined as follows: \begin{enumerate}
\item Work under the linear order on $[n]$, $<_{v+1}$ or $<_w$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$.
\item There is a propagator $s_1 \in P_v$ and $s_4 \in P_w$ defined such that $s_4 = (i_{s_4}, v)$ and $s_1 = (i_{s_1}, v)$. One may also have $s_1 = (i_{s_1}, v-1)$. Furthermore, $s_m \in [i_p, v]$.
\item For the given $a$, either $a-3 <_{v+1} i_{s_1}$ or there exist $2$ propagators $s_2$ and $s_3 \in P_v$ such that $s_3 = (i_{s_3}, i_{s_1})$ and $s_2 = (i_{s_2}, i_{s_1})$. One may also have $s_2 = (i_{s_2}, i_{s_1}-1)$. Furthermore, $a-3 <_{v+1} s_m$.\end{enumerate}
\end{dfn}

\begin{lem}\label{protecting lem}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$, and $a \in [n]$ be a vertex. If there exists a $P_v$, for $v \in \{i,j\}$, then $p$ does not contribute $v$ to $I_a$. If there are two sets $P_v$ and $P_w$, for $w \in \{i+1, j+1\}$, then $p$ does not contribute $w$ to $I_a$.
\end{lem}

\begin{proof}
We consider first the case of $p$ not contributing $v$ to $I_a$.

The set $P_v$ is constructed such that, $s_1$ if it exists at step $v$ of Algorithm \ref{alg:put GN on WLD}, prevents $p$ from contributing $v$ to $I_a$. By the positioning of $a$, either the algorithm does not encounter the propagators $s_1$ before vertex $v$ or $v-1$, or it encounters it at $i_{s_1}$.  In this case, the existence of $s_2$ and $s_3$ prevent $s_1$ from contributing at vertices $i_{s_1}$ or $i_{s_1}+1$. Therefore, $s_1$ remains in the diagram at step $v$.

If both $P_v$ and $P_w$ exists, then if $s_1$ and $s_3$ exist at step $v$ of Algorithm \ref{alg:put GN on WLD}, prevents $p$ from contributing $v$ and $w$ to $I_a$. By the positioning of $a$, either the algorithm does not encounter the propagators $s_1$ and $s_4$ before vertex $v$ or $v-1$, or it encounters only $s_1$ before $v$ or $v-1$. By the above argument, $s_1$ remains in the diagram at step $v$. Finally, the algorithm may encounter $s_4$ at $i_{s_4}$. In this case, the existence of $s_5$ and $s_6$ prevent $s_4$ from contributing at vertices $i_{s_4}$ or $i_{s_4}+1$. Therefore, $s_4$ remains in the diagram at step $v$.   Thereofre, in this case, $p$ cannot contribute either $v$ or $v+1$ to $I_a$.
\end{proof}

There is an easy corrollary to this, describing when propagators cannot contribute certain vertices to elements of the Grassman necklace.

\begin{cor} \label{protecting cor}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$. Picking a $v \in \{i, j\}$ write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$. If $a \in [j_p+1, i_p+1]$ then no protecting set $P_v$ or $P_w$ can protect $p$ at $v$ or $v+1$ from $a$.
\end{cor}

\begin{proof}
Since $W$ is admissible, it cannot have crossing propagators. Therefore niether $P_v$ cannot have the requisite propagator $s$ with $a-3 <_{v+1} i_s$.
\end{proof}

The converse, howevever requires an extra condition.

\begin{lem} \label{protect conv lem}
For $W = (\cP, n)$, $p = (i,j)$, and $v \in \{i, j\}$, $w \in \{i+1, j+1\}$ and $ a \in [n]$ a vertex of $W$, if $v$ (resp. $w$) is the first vertex of $V_p$ in the $<_a$ order such that $P_v$ (resp. neither $P_v$ nor $P_w$) does not exsist, then $p$ contributes $v$ (resp. $w$) to $I_a$.
\end{lem}

\begin{proof}
If $p$ doesn't contribute $v$ or $w$ $I_a$, then either $p$ contributes a different supporting vertex $u$ earlier in the $<_a$ order or there is a propagator at $s_1$ preventing $p$ from contributing $v$ (or $w$) to $I_a$, or there is a pair of propagators $s_1$ (resp. and $s_4$) preventing $p$ from contributing $w$, or $v$, at $I_a$.

If there is a propagator $s_1 \in \cP$ that are still in the diagram at step $v$, (write them $s_1 = (i_{s_1}, j_{s_1})$ with $j_{s_1} \in \{v, v-1\}$), then $s_1$ did not contribute $i_{s_1}$ or $i_{s_1} +1 $ to $I_a$. Therefore, $s_1$ cannot contribute $i_{s_1}$ $i_{s_1}+1$ to $I_a$. In other words, either $a-3 <_{v+1} i_{s_1}$ or there must be two other propagators $s_2 = (i_{s_2}, j_{s_2})$ and $s_3 = (i_{s_3}, j_{s_3})$, with $j_{s_2} \in \{i_{s_1}, i_{s_1}-1\}$ and $i_{s_3} <_{s_1} i_{s_2} <_{s_1} j_{s_2} \leq_{s_1} j_{s_3} = j_{s_1}$ that prevent this. We show that, if $a-3 \not <_{v+1} i_{s_1}$, then $a-3 <_{v+1} i_{s_2} <_{v+1} s_3$. That is, there is a set $P_v$ preventing $p$ from contributing $v$.

The argument for showing that there must be two sets $P_v$ and $P_w$ is simlar, and is not made explicit here.

We proceed by contradiction. Suppose $a-3 \not <_{v+1} i_{s_2}$. Then, there exists two propagators $s_4$ and $s_5$ such that $s_4 = (i_{s_4}, j_{s_4})$ and $s_5 = (i_{s_5}, j_{s_5})$, with $j_{s_4} \in \{i_{s_2}, i_{s_2}-1\}$ and $i_{s_5} <_{s_2} i_{s_4} <_{s_2} j_{s_4} \leq_{s_2} j_{s_5} = j_{s_2}$. If $a-3 <_{v+1} i_{s_4} <_{v+1} s_5$, we may assume without loss of generality that there are no futher propagators of the form $t = (i_t, j_t)$ with $j_t \in \{i_{s_1}, j_{s_1}-1\}$ or $i_t \in [ i_{s_4}, i_{s_1}]$. Otherwise, one may replace $p$ with $s_1$ in this argument. Therefore, $s_1$ contributes $i_{s_1}$ to $I_a$, which is a contradiction. Therefore, we must again suppose that $a-3 \not <_{v+1} i_{s_4}$.

In order for $s_1$ to exists at step $v$ of algorithm \ref{Alg:put GN on WLD}, one must continue to find pairs of propagators $s_{m'}$, $s_{m'+1}$ in $\cP$ that sheild the initial endpoint of a previously defined propagator, $s_m$. There are three cases to consider. Let $s_k$ indicate a propagator identified at an earlier stage of this construction where $i_{p_0} = \min{i_p, a}$.

 \begin{description}
\item[$i_{s_m} = i_{p_k}+2$] By admissibility, there is not room to place both the propagators $s_{m'}$, and $s_{m'+1}$. Thus $s_m$ is removed at the step $i_{s_m}$ or $i_{s_m} + 1$. Therefore, $s_1$ contributes at either $i_{s_1}$ or $i_{s_1}+1$.
 \item[$i_{s_m} = i_{p_k}+1$] By admissibility, there is not room to place either the propagators $s_{m'}$, or $s_{m'+1}$. Thus $s_m$ is removed at the step $i_{s_m}$. Therefore, $s_1$ contributes at either $i_{s_1}$ or $i_{s_1}+1$.
 \item[$i_{t_m} = i_{p_k}$] Since $k < m$, the propagator $p_k$ is not removed at step $i_{p_k}$ or $i_{p_k}+1$. Therefore neither is $s_{m'}$. Furthermore, there cannot be propagators that prevent $s_{m'}$ from being removed at $j_{s_m}$ or $j_{s_m}+1$. Otherwise, we could replace $p$ with $sm_{m'}$ and repeat this argument. Since $\cP$ is finite, this replacement process must terminate, forcing $s_{m'}$ to contribute $j_{s_m}$ or $j_{s_m}+1$, and thereby, $s_1$ contributes at either $i_{s_1}$ or $i_{s_1}+1$.
 \end{description}
\end{proof}

@@

Since $p$ is not removed by step $j+1$, by Lemma \ref{protect dfn lem} there are $4$ protecting sets, $P_i,P_{i+1}, P_{j}$ , and $P_{j+1}$ respectively, allowing $p$ to remain after $n$ steps.

@@

\begin{lem} \label{vertex cyclic int lem}
For every $v \in V_p$, there is a non-empty cyclic interval such that $p$ contributes $v$ to all $I_{a}$ for in said interval.
\end{lem}

@@

Let $k_1 \ldots k_r$ be the set of propagators ending on edge $j$ or $j-1$, ordered such that $k_1$ is the first propagators clockwise from $p$, and $k_r$ is the clockwisemost propagator on edge $j-1$. For each $k_x$, write $P_{x} = \{k_x, s_x, t_x\}$, where $s_x$ and $t_x$, if they  exist, to be the two clockwise most propagators preventing $k_x$ from contributing $j$ to $I_{i+2}$. Similarly, let $l_1 \ldots l_m$ be the set of propagators ending on edge $i$ or $i-1$, ordered such that $l_1$ is the first propagators clockwise from $p$, and $l_m$ is the clockwisemost propagator on edge $i-1$. For each $l_y$, write $Q_{y} = \{l_x, s_y, t_y\}$, where $s_y$ and $t_y$, if they  exist, to be the two clockwise most propagators preventing $l_y$ from contributing $i$ to $I_{j+2}$.

>>>>

\pgfmathsetmacro{\n}{#1}
\pgfmathsetmacro{\radius}{#2}
\pgfmathsetmacro{\angle}{360/\n}
\draw (0,0) circle (\radius);
    \foreach \i in {1,2,...,\n} {
      \draw (\angle*\i:\radius) node {$\bullet$};
       %\pgfmathsetmacro{\x}{\angle*\i}
       %\draw[-,shorten >=-\radius*0.1 cm,shorten <=-\radius*0.1 cm]  (\x:\radius cm)-- (\x + \angle: \radius cm);
    }

\newcommand{\drawpolypart}[2]{
\pgfmathsetmacro{\n}{#1}
\pgfmathsetmacro{\radius}{#2}
\pgfmathsetmacro{\angle}{360/\n}
    \foreach \i in {1,2,...,\n} {
      \draw (\angle*\i+ \angle/2:\radius) node {$\bullet$};
      \pgfmathsetmacro{\x}{\angle*\i - \angle/2}
      \pgfmathsetmacro{\concave}{((\n-1.5)/\n)}
      \draw (\x:\radius cm) .. controls (\angle *\i: \concave* \radius cm) .. (\x + \angle:\radius cm);
      %\draw (\angle *\i: .8* \radius cm) node {$\bullet$};
    }

@@

\begin{scope}
%\clip (\angle*\r:\radius) -- (\angle + \angle*\r:\radius) -- (\angle*\s:\radius) -- (\angle + \angle*\s:\radius) -- (\angle*\r:\radius);
\draw[propagator] (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius) -- (\angle*\s + \angle/2 + \bumps*\perturbe:\radius);
\end{scope}
}

\newcommand{\drawlabeledprop}[5]{
\pgfmathsetmacro{\r}{#1}
\pgfmathsetmacro{\bumpr}{#2}
\pgfmathsetmacro{\s}{#3}
\pgfmathsetmacro{\bumps}{#4}
\pgfmathsetmacro{\perturbe}{\angle/\n}

\begin{scope}
%\clip (\angle*\r:\radius) -- (\angle + \angle*\r:\radius) -- (\angle*\s:\radius) -- (\angle + \angle*\s:\radius) -- (\angle*\r:\radius);
\draw[propagator] (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius) -- (\angle*\s + \angle/2 + \bumps*\perturbe:\radius) node[midway, below] {#5};
\end{scope}
}

\newcommand{\drawchord}[2]{
\pgfmathsetmacro{\r}{#1}
\pgfmathsetmacro{\s}{#2}

\begin{scope}
%\clip (\angle*\r:\radius) -- (\angle + \angle*\r:\radius) -- (\angle*\s:\radius) -- (\angle + \angle*\s:\radius) -- (\angle*\r:\radius);
\draw (\angle*\r + \angle/2:\radius) -- (\angle*\s + \angle/2:\radius);
\end{scope}
}

@@

\newcommand{\drawnumbersshift}{
  \foreach \i in {1,2,...,\n} {
  \pgfmathsetmacro{\x}{\angle*\i + \angle/2}
  \draw (\x:\radius*1.15) node {\footnotesize \i};
}
}

@@

\begin{eg} \label{eg:equivdiags}
Note that since this is an equivalence relation, we may find that two Wilson loop diagrams are equivalent, even if they do not have complements of (non-trivial) exact subdiagrams in common. Consider the following three Wilson loop diagrams,
\bas
W_1 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{8}{1.5}
	\drawnumbers
	\drawprop{1}{0}{4}{0}
	\drawprop{2}{0}{4}{-1}
    \drawprop{5}{0}{8}{0}
    \drawprop{5}{1}{7}{0}
		\end{scope}
	\end{tikzpicture} \quad
W_2 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{8}{1.5}
	\drawnumbers
	\drawprop{1}{0}{4}{0}
	\drawprop{2}{0}{4}{-1}
    \drawprop{5}{0}{8}{0}
    \drawprop{6}{0}{8}{-1}
		\end{scope}
	\end{tikzpicture} \quad
W_3 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{8}{1.5}
	\drawnumbers
	\drawprop{1}{0}{4}{0}
	\drawprop{1}{1}{3}{0}
    \drawprop{5}{0}{8}{0}
    \drawprop{6}{0}{8}{-1}
		\end{scope}
	\end{tikzpicture} .
\eas

@@

\begin{eg}
For example, ordering the propagators of $W_1$ from Example \ref{eg:equivdiags}: \bas (1,4), \, (2,4), \, (5,7), \, (5,8) \eas we may write
\bas C(W_1) = \left(
\begin{array}{cccccccc}
c_{1,1} & c_{1,2} & 0 & c_{1,4} & c_{1,5} & 0 & 0 & 0 \\
0 & c_{2,2} & c_{2,3} & c_{2,4} & c_{2,5} & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & c_{3,5} & c_{3,6} & c_{3,7} & c_{3,8} \\
c_{4,1} & 0 & 0 & 0 & c_{4,5} & c_{4,6} & 0 & c_{4,8}  \\
\end{array}
\right) \;.\eas

@@

\begin{eg}\label{WLDtopolygonpartition}
In this example we return to the Wilson loop diagrams in Example \ref{eg:equivdiags}. We can pair diagrams with their polygon partitions as follows:
\bas W_1 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{8}{1.5}
	\drawnumbers
	\drawprop{1}{0}{4}{0}
	\drawprop{2}{0}{4}{-1}
    \drawprop{5}{0}{8}{0}
    \drawprop{5}{1}{7}{0}
		\end{scope}
	\end{tikzpicture} \quad; \quad
\tau(W_1) = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawpolypart{8}{1.5}
    \drawnumbersshift
    \drawchord{1}{4}
    \drawchord{2}{4}
    \drawchord{5}{8}
    \drawchord{5}{7}
	\end{scope}
	\end{tikzpicture}
\eas and
\bas W_3 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{8}{1.5}
	\drawnumbers
    \drawprop{1}{0}{4}{0}
	\drawprop{1}{1}{3}{0}
    \drawprop{5}{0}{8}{0}
    \drawprop{6}{0}{8}{-1}	
		\end{scope}
	\end{tikzpicture}\quad; \quad
\tau(W_3) = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawpolypart{8}{1.5}
    \drawnumbersshift
    \drawchord{1}{4}
    \drawchord{1}{3}
    \drawchord{5}{8}
    \drawchord{6}{8}
	\end{scope}
	\end{tikzpicture} .
\eas

@@

\begin{eg} \label{eg: unique decomposition} For the Wilson loop diagrams and polygon partitions in example \ref{WLDtopolygonpartition}, the vertex sets $\{1, 2, 3,4\}$ and $\{5, 6, 7, 8\}$ are maximal triangulated pieces for both $\tau(W_1)$ and $\tau(W_3)$. The vertex set $\{4,5, 8, 1\}$ is not a triangulation in either polygon partition. \note{do we want a picture of a dual tree here? Being lazy}
\end{eg}

@@

If $n=2$, then $t$ has two connected components. Therefore, $t$ corresponds to a propagator that connects two non-adjacent edges. Therefore, the trivial triangulation is a trivial exact subdiagram.

@@

\begin{enumerate}
\item Fix a vertex $a \in [n]$. Set $i:=a$ and $I_a = \emptyset$.
\item While $\cP \neq \emptyset$, perform the following steps.
\begin{enumerate}
\item \textbf{Step $i$ for vertex $a$}: If $\Prop(i) \neq \emptyset$ in $W$, write $I_a = I_a \cup i$. Let $p \in \Prop(p)$ be the clockwise most propagator supported on $i$. Write $W = (\cP \setminus p, n)$.
\item If $Prop(i) = \emptyset$ do nothing.
\item Increment $i$ by 1 and repeat from (a).
\end{enumerate}
\end{enumerate}
\end{algorithm}

@@

\begin{dfn}\label{protect dfn}
Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex. For $p= (i,j) \in \cP$ an a propagator of $W$  and $v \in \{i, j\}$ a vertex of $W$, let $P_{v}(p)$ or $P_{v+1}(p)$ to be two \emph{protecting sets of $p$ at $v$ and ${v+1}$} be a set of propagators defined as follows: \begin{enumerate}
\item Work under the linear order on $[n]$, $<_{v+1}$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$.
\item If there is a propagator $s_1 \in \cP$ such that $s_1 = (i_{s_1}, v)$ or $s_1 = (i_{s_1}, v-1)$, then $s_1 \in P_v(p)$.
\item If $s_1$ as above does not exists, then $P_v(p) = \emptyset$. In this case, $P_w(p) = \emptyset$. When $P_v(p) \neq \emptyset$, if there exists a propagator $t_1 \in \cP$ defined such that $t_1 = (i_{t_1}, v)$ and $s_1 = (i_{s_1}, v)$ with $i_p <_{v+1} i_{t_1} <_{v+1} i_{s_1}$, $P_w(p) = t_1$.
\item If $s_1 = (i_{s_1}, v)$ then \bas P_v(p)=  \begin{cases} \{s_1\} \cup P_{i_{s_1}}(s_1) \cup P_{i_{s_1}+1}(s_1) & \textrm{ if } P_{i_{s_1}+1}(s_1) \neq \emptyset \\ s_1 &  \textrm{ else } \end{cases}. \eas  If $s_1 = (i_{s_1}, v-1)$ then \bas P_v(p)=  \begin{cases}  \emptyset & \textrm{ if } P_{v-1}(s_1) = \emptyset \\ \{s_1\} \cup P_{v-1}(s_1) & \textrm{ else } \end{cases} \eas.
\end{enumerate}
\end{dfn}

The protective sets $P_\cdot(p)$ are designed to prevent $p$ from contributing the vertex indicated in the subscript at certain points in the Grassmann Necklace, $I_a$. Write $P_v(p) = \{s_1, \ldots s_r, t_2,  \ldots t_r\}$ with the $t_x = P_{i_{s_{x-1}}+1}(s_{x-1})$ and $s_x \in P_{i_{s_{x-1}}}(s_{x-1})$ for $x \geq 2$. We place the restrictions on the vertex $a$ as follows: \begin{enumerate} \item $P_v$ prevents $p$ from contributing to $I_a$ if \bas i_{s_r}  <_{v+1} a-1 <_{v+1} v\eas \item $P_{v+1}(p)$ prevents $p$ from contributing to $I_a$ only if $P_v(p)$ prevents $p$ from contributing $v$ to $I_a$. \end{enumerate}

\begin{eg} \label{eg: protective sets}
Consider the admissible Wilson loop diagram
\bas W=\begin{tikzpicture}[rotate=120,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{17}{3}
	\drawnumbers
	\drawprop{1}{0}{16}{0}
	\drawlabeledprop{2}{0}{15}{1}{p}
    \drawprop{6}{2}{15}{0}
    \drawprop{3}{0}{6}{1}
    \drawprop{4}{0}{6}{0}
    \drawprop{7}{0}{11}{0}
    \drawprop{8}{0}{10}{0}
    \drawprop{11}{1}{14}{1}
    \drawprop{12}{0}{14}{0}
		\end{scope}
	\end{tikzpicture}
\eas Consider the two sets of propagators $Q = \{(3, 6), (4, 6), (6,15)\}$ and $R = \{ (7, 11), (8, 10), (11, 14), (12, 14)\}$. The propagator $p = (2, 15)$ is protected at $a = 5$ from contributing $15$ to $I_5$ by the set $P_{15} = Q$. There is no set preventing $p$ from contributing $16$ to $I_{15}$. At $a = 9$, the set $P_{15} = \{(6,15)\} \subset Q$. We may just as easily right $P_{15} = Q$, though the other two propagators in the set prove unnecessary to keep $p$ from contributing $15$ to $I_{9}$. At $a = 14$, both $P_{15}$ and $P_{16}$ exists, with $P_{15} = \{(11, 14), (12, 14)\} \subset R $ and $P_{16}= \{(6,15)\} \subset Q$. We may just as easily right $P_{15} = R$ and $P_{16} = R$, though the other two propagators in each set are unnecessary.

Note that for $a=1$, the propagator $p$ contributes $2$ to $I_1$. However, in this case, we say that neither $P_{15}$ or $P_{16}$ exist.
\end{eg}

\begin{lem}\label{protecting lem}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$, and $a \in [n]$ be a vertex. For $v \in \{i,j\}$, if $P_v(p) \neq \emptyset$, write $P_v(p) = \{s_1 \ldots s_r, t_2, \ldots t_r\}$ as above. Then $p$ does not contribute $v$ to $I_a$ if $i_{s_r} +1 <_{v+1} a <_{v+1} v+1 $. If both $P_v(p)$ and $P_{v+1}(p)$ are non empty, then $p$ also does not contribute $v+1$ to $I_a$.
\end{lem}

\begin{proof}
Note that if $s_1 \in P_v(p)$ exists at step $v$ of Algorithm \ref{alg:put GN on WLD}, then $p$ cannot contribute $p$ to $I_a$. Further, if $P_{v+1}(p) \neq \emptyset$, $p$ cannot contribute $v+1$ to $I_a$ either.

Next we show that if $P_v(p)$ is as above, with $i_{s_r}+1 <_{v+1} a$, then the propagator $s_1$ exists at step $v$ of Algorithm \ref{alg:put GN on WLD}. Let $x$ be the largest integer that such that $a <_{v_1} j_{x}+1$. Then $s_x$ cannot contribute to $I_a$ before vertex $v$. By construction $P_{i_{s_x}+1}(s_{x-1})\subset P_v(p)$. Therefore, $s_{x-1}$ does not contribute $i_{s_x}+1$ to $I_a$. Thus we conclude that $s_1$ does not contribute $i_{s_1}$ or $i_{s_1}+1$ to $I_a$. In other words, $s_1$ has not been removed from the diagram at vertex $v$.

Thus we say that $P_v(p)$ protects $p$ at $v$ from $a$, for $a \in [i_{s_r}+2, v]$. There is an easy corollary to this, describing when such a protecting set cannot exist.

\begin{cor} \label{protecting cor}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$. Picking a $v \in \{i, j\}$ write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$. If $a \in [j_p+1, i_p+1]$ then there can be no protecting set $P_v$ or $P_{v+1}$ protecting $p$ at $v$ or $v+1$ from $a$.
\end{cor}

\begin{proof}
Since $W$ is admissible, it cannot have crossing propagators. Therefore neither $P_v$ cannot have the requisite propagator $s_r$ with $i_{s_r}+1  <_{v+1} a$.
\end{proof}

The converse, however requires an extra condition.

\begin{lem} \label{protect conv lem}
For $W = (\cP, n)$, $p = (i,j)$, and $v \in \{i, j\}$ and $ a \in [n]$ a vertex of $W$, if $v$ (resp. $v+1$) is the first vertex of $V_p$ in the $<_a$ order such that $P_v$ (resp. neither $P_v$ nor $P_{v+1}$) does not exist, then $p$ contributes $v$ (resp. $v+1$) to $I_a$.
\end{lem}

\begin{proof}
Write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$.

If $p$ doesn't contribute $v$ (or $v+1$) to $I_a$, then either $p$ contributes a different supporting vertex $u$ earlier in the $<_a$ order or there is a propagator $s_1$ at step $v$ of the algorithm \ref{alg:put GN on WLD} preventing $p$ from contributing $v$ to $I_a$, (or there are a pair of propagators $s_1$ and $t_1$ at step $v$ preventing $p$ from contributing $v+1$ at $I_a$.)

If there are propagators $s_1, t_1 \in \cP$ that are still in the diagram at step $v$, (write them $s_1 = (i_{s_1}, j_{s_1})$, and $t_1 = (i_{t_1}, j_{t_1})$) with $j_{s_1} \in \{v, v-1\}$, and $i_p \leq_{v+1} i_{t_1} <_v i_{s_1} <_v j_{s_1} \leq_{v} j_{t_1} = v$) then $s_1$ or $t_1$ did not contribute $i_{s_1}$ or  $i_{s_1} +1 $ (resp. $i_{t_1}$ or $i_{t_1}+1$) to $I_a$. Then one of the following three situations hold: \begin{enumerate} \item $i_{s_1}+1 <_{v+1} a$ and $j_{s_1} = v$: In this case, $s_1$ cannot be removed until $v$. \item $i_{s_1}+1 <_{v+1} a$ and $j_{s_1} = v-1$: in this case there exists a propagator $s_2 = (i_{s_2}, j_{s_2})$ with $i_{s_1} \leq_{v+1} i_{s_2} <_{v+1} j_{s_2}$ and $j_{s_2} \in \{j_{s_1}-1, j_{s_1}\}$. \item $i_{s_1}+1 \not <_{v+1} a$ and $j_{s_1} = v$: and there must be two other propagators $s_2 = (i_{s_2}, j_{s_2})$ and $t_2 = (i_{t_2}, j_{t_2})$, with $j_{s_2} \in \{i_{s_1}, i_{s_1}-1\}$ and $i_{s_1} \leq_{v+1} i_{t_2} <_{v+1} i_{s_2} <_{v+1} j_{s_2} \leq_{v+1} j_{t_2} = j_{s_1}$   \end{enumerate}

However, now one must ensure that the newly identified propagators $s_2$ and $t_3$ do not contribute to $I_a$ before $i_{s_1}$. One does this by a similar construction to above. In this manner, we begin to build the sets $P_v(p)$ and $P_{v+1}(p)$.  By finiteness and admissiblity of the Wilson loop diagram, both these sets are finite; one cannot continue to add propagators $s_i$, $t_i$ ad infinitum.

We claim that this implies that at some point there is a terminal propagator, $s_m \in P_v(p)$ such that $i_{s_m} + 1 <_{v+1} a$, and \bas  \textrm{ either }= \begin{cases} j_{s_m}=i_{s_{m-1}} & \textrm{ }\\ j_{s_m}=j_{s_{m-1}} & \textrm{ } \end{cases} .\eas We show that all other possibilities lead to a contradiction. For the remainder of this proof, indicate by $p_k$ some propagator identified at an earlier stage of this construction. That is, for $0 < k < m$, $p_k \in \{s_k, t_k\}$. Futher define $p_0 = p$.

%\begin{cases} j_{s_{m}=i_{s_{m-1}} & \textrm{ } \\  j_{s_m}=j_{s_{m-1}} & \text{ }\end{cases}

If $j_{s_m} \in \{i_{s_{m-1}}-1, j_{s_{m-1}}-1\}$, then, this cannot be the final propagator added to $P_v(p)$, as one would need a means of preventing $s_m$ from contributing $i_{s_{m-1}}-1$ or $j_{s_{m-1}}-1$ to $I_a$.

If $i_{s_m} + 1 \not <_{v+1} a$, then there are two.
 \begin{description}

\item[$j_{s_m} = i_{s_{m-1}}$ and $i_{s_m} \in \{i_{p_k}+2, i_{p_k}+1\}$] for some $k<m$. By admissibility, there is not room to place both the propagators $s_{m+1}$, and $t_{m+1}$. Thus $s_m$ is removed at the step $i_{s_m}$ or $i_{s_m} + 1$. Therefore, $s_1$ contributes at either $i_{s_1}$ or $i_{s_1}+1$. This leads to a contradiction.
\item[$j_{s_m} = i_{s_{m-1}}$ and $i_{s_m} = i_{p_k}+2$] for some $k<m$. This requires either crossing propagators or propagators starting and ending at the same edge, which violates admissibility.
 \end{description} \note{correct but clear as mud? Help?}
\end{proof}

@@

Since $p$ is not removed by step $j+1$, by Lemma \ref{protecting lem} there are $4$ protecting sets, $P_i,P_{i+1}, P_{j}$ , and $P_{j+1}$ respectively, allowing $p$ to remain after $n$ steps.

@@

\begin{lem} \label{vertex cyclic int lem}
For every $v \in V_p$, Let $A_v \subset [n]$ be the set of vertices where $p$ contributes $v$ to $I_a$. Then $A_v$ is a non-empty cyclic interval.
\end{lem}

@@

Let $k_1 \ldots k_r$ be the set of propagators of the form $k_x = (i_{k_x}, j)$, with $i <_{j+1} k_1 <_{j+1} \ldots k_r <_{j+1} j$. Write $k_{r+1}$ to be the counterclockwise most propagator with an end on the edge $j-1$, if it exists. If $r \geq 2$ or $r+1 = 2$, then both $P_j(p)$ and $P_{j+1}(p)$ exists for some subset of $a \in [n]$. If $r=1$ or $r+1= 2$ then only $P_j(p)$ exists. Otherwise, $P_j(p) = \emptyset$.
